Reproducibility of HCP pipelines across operating systems

### 2017-06-14 paper.tex
Added Freesurfer installation details

>>>>

\subsection{FreeSurfer Docker container}

For the creation of Docker container contianer the FreeSurfer Pipelines, there are a few prerequisites. They are

\begin{itemize}
  \item 64 Bit Operating System (We chose Centos 5, 6 and 7)
  \item FMRIB Software Library(a.k.a FSL) version 5.0.6 (An installation script was developed for this)
  \item Freesurfer version 5.3.0-HCP
  \item Connectome Workbench
\end{itemize}

Out of the images having PreFreeSurfer and environment variables available in Dockerhub(https://hub.docker.com/u/bigdatalabteam/dashboard/), we installed FreeSurfer. FreeSurfer(ftp://surfer.nmr.mgh.harvard.edu/pub/dist/freesurfer/5.3.0-HCP/freesurfer-Linux-centos4\_x86\_64-stable-pub-v5.3.0-HCP.tar.gz) was used for installation. SetUpFreeSurfer script should be sourced before running the FreeSurferPipelineBatch script. There were a few missing libraries that are added using yum to the base image o f the centos since these libraries are used by FreeSurfer Pipeline. The images which are input to the FreeSurfer should be processed using PreFreeSurfer. FreeSurfer needs a license number which is obtained from the FreeSurfer site and it is essential for smooth functioning of FreeSurfer.
